\section{INTELLIGENCE}

On the strategic map, neither side may examine his opponent's units unless certain conditions apply.

A player may deploy his units face down on the strategic map. Exception: Civis units are always deployed on the side controlling the city.

A player may not examine enemy forces or units unless one of the following conditions apply:

He plays an Agent Stratagem Marker for an Intelligence mission.
A friendly unit enters the hexagon.
An enemy force enters a hexagon containing friendly units.
During combat.
A player voluntarily reveals his forces.

If any of the above conditions occur, the force is flipped to its front side and the enemy player may examine it. The force remains face up, and the enemy may continue to examine it, until the beginning of the friendly player's next turn, at which point any friendly forces or units may again be inverted.

\subsection{Exercitus (Army) Markers}

Each side has three Exercitus markers. These are used as substitute counters. A player may at any time in his turn replace a force on the map with an Exercitus marker, and place those units in the same numbered Exercitus Holding Area for his side. The enemy may not examine the contents of an Exercitus Holding Area, unless the conditions above apply.

Civis units may not be part of an Exercitus.

Note that the Parthian Exercitus markers are blue. However, the Parthian player can use them to represent any of his units, including the tan or green units.

An Exercitus may contain zero units and be used as a way to bluff the opposing player. If revealed for any reason, the Exercitus Marker is removed from the map. However, the player may immediately place it on any friendly unit.

\subsection{Battle Map Display}

Units are always deployed face up when they are deployed on either the Basic Game Battle/Siege Displays (or the Advanced Game Battle Board).

A player may deploy his forces and markers face down when on any of the other game displays (i.e., his recruit/off-map/exercitus/stratagem marker holding areas). Players may place a sheet of paper (or whatever) over their Holding Areas to further conceal their forces from the enemy.

Units in the Client holding area are always deployed face up. Units in the Civis Holding Area may be on either side, inasmuch as they have no limited intelligence status.

A player may examine an enemy Holding Area only by playing an Agent Stratagem marker (see player aid card for details). A player may always examine his own units.

The intelligence rules are mandatory. Ancient warfare cannot be understood unless the factor of limited intelligence is accounted for. Any player who violates the intelligence rules automatically forfeits the game and is permanently disgraced.
