\clearpage

\section{SCENARIOS}

\subsection{Scenario 1: The Armenian War}

\begin{flushleft}
Game Length:\\
\qquad Start: April, 114 AD\\
\qquad End: Winter I, 114 AD
\end{flushleft}

Initial Forces:

{
  \titleformat
  {\subsubsection}
  [hang]
  {\bfseries}
  {\arabic{section}.\arabic{subsection}.\arabic{subsubsection}}
  {0.3em}
  {}

  \subsubsection{Romans}
}


\textbf{Antioch}: Leaders Trajan, Hadrian; Legions IV Sc, VI Fe, II Tr; Vexillation Praetorian Heavy Cavalry ESA, ESS, Moor; Impeditus I.

\textbf{Any Roman cities within 4 hexes of Antioch:} Auxiliary infantry I Syr, II Syr, III Syr; Equites Cavalry I Syr, II Syr, III Syr, Equites A. Drom S.

\textbf{Caesarea:} Leader Quietus; Legion X Fr.

\textbf{Any Roman cities within 3 hexes of Caesarea:} Auxiliary infantry I Pal, II Pal; Equites Pal.

\textbf{Bostra:} Legion III Ga; Auxiliary infantry Ar; Equites Ar; Ala Drom A.

\textbf{Mazaca and/or Tarsus:} Leader Junius; Legions XVI FF, XII Fu.

\textbf{Any city within 4 hexes of Mazaca:} Auxiliary Infantry I Cap and II Cap; Equites I Cap and II Cap.

\textbf{Palmyra:} Horse archer Palmyra.

\textbf{Any Roman controlled city:} Vexillations Frum I, Frum II, Frum III, Impeditus II, Impeditus III; Light infantry Numeri; Leaders Clarus, Alexander, Severus, Santra.

\textbf{Any Roman controlled coastal city:} Vexillation Classici.

\textbf{Off Map Forces:} Legionary Vexillations I Ad, I It, III Cy, V Ma, VII Cl, XI Cl, XIII Ga, XV Ap, XXII Ul; Auxiliary infantry Aeg, Dan; Equites Aeg, Dan.

\textbf{In Recruiting Pool:} Leaders Sentius, Legate; CICR, C Vol; Auxiliary infantry I Orient, II Orient. Horse archer Syrorum.

\textbf{Roman Civis:} all Roman cities; Egra and Thaema (Arabian cities).

\textbf{Strategem Markers:} Romans receive three Strategem Markers, drawn at random.

\pagebreak
{
  \titleformat
  {\subsubsection}
  [hang]
  {\bfseries}
  {\arabic{section}.\arabic{subsection}.\arabic{subsubsection}}
  {0.3em}
  {}

  \subsubsection{Parthians}
}

\textit{Core}

\textbf{Ctesiphon:} Leader Chosroes; Court; Cataphract Companions, Guards.

\textbf{In any Parthian city other than a capital, no more than one per city:} Parthamaspates, Meherdotes, Sanatruces, Vologases.

\textbf{In any Parthian City west of Ctesiphon:} Horse archer Mesopotamia.

\textbf{In any Parthian City north of Ctesiphon:} Horse archer Media.

\textbf{In any Parthian City south of Ctesiphon:} Horse archer Persis.

\textbf{In any Parthian City east of Ctesiphon:} Horse archer Hyrcania.

\textbf{Core Recruiting Pool:} Impeditus

\textbf{Satrapy Recruiting Pool:} Leaders Surenas, Karen, Gew and Mihran; cataphracts I through VIII and C. Drom; horse archers I through XII; levy infantry I through IV; elephant

During initial setup, the Parthian player draws at random four satraphy units from the reinforcement pool and places one each with the leaders Parthamaspates, Meherdotes, Sanatruces, and Vologases.

\textbf{Parthian Civis:} all Parthian cities; the two Armenian cities; Dumaetha (Arabian).

\textbf{Strategem Markers:} None.

\textbf{Client Forces}

\textbf{Armenia} (Parthian Client):

In Artaxata: Cataphract; Horse Archer; Auxiliary infantry; Leader Parthamisiris.

\textbf{Arabs} (Advanced rules only): neither player's client.

Recruiting Pool: Horse archers.

\textbf{Alani} (Optional rules only): neither player's client.

Recruiting Pool: Horse archers.

\textbf{Special Rule:} In addition to the standard victory conditions, each Armenian city counts as five cities for satisfying condition "c" of the Victory Conditions.