\section{SEQUENCE OF PLAY}

Trajan is played in consecutive game turns, with each player conducting operations in his own turn. The overall structure of the game is as follows:

\subsection{Game Years}

Each year consists of six Campaign turns (April, May, June, July, August, September) and two Winter turns (October-December and January-March). This is shown on the Turn Record track.

\subsection{Campaign and Winter Turn segments}

\subsubsection{Political Events Segment}

Two dice are rolled, the players check the Political Events Table, and apply the result.

\subsubsection{Roman Turn}

\begin{itemize}
  \item \textbf{Stratagem Marker segment:} the Roman player draws a number of Stratagem Markers as designated.
  \item \textbf{Movement segment:} The Roman player attempts to move his units; he may also play Stratagem Markers for certain game functions.
  \item \textbf{Combat segment:} The Roman player conducts battles and sieges.
  \item \textbf{Supply Segment (Advanced Game only):} The Roman player checks supply for applicable units.
\end{itemize}

\subsubsection{Parthian Turn}

\begin{itemize}
  \item \textbf{Stratagem Marker segment:} the Parthian player draws a number of Stratagem Markers as designated.
  \item \textbf{Movement segment:} The Parthian player attempts to move his units; he may also play Stratagem Markers for certain game functions.
  \item \textbf{Combat segment:} The Parthian player conducts battles and sieges.
  \item \textbf{Supply Segment (Advanced Game only):} The Parthian player checks supply for applicable units.
\end{itemize}

\subsection{Completion of the Turn}

Once both players have completed their turns, the Game Turn ends and a new one begins. Play continues until the end of the scenario, one side capitulates, or both players agree to a Treaty.

\subsection{Winter Turns}

Winter turn are conducted the same as Campaign turns, except that there are additional penalties for movement and supply.