\section{THE BASIC GAME RULES}

\subsection{INTRODUCTION}

The Basic Game is the easiest to learn and least complicated version of SHENANDOAH. It is ideal for players who prefer relatively simple and straightforward games, and also serves as an introduction to the game's mechanics for players who prefer more complex games and will eventually wish to try the Advanced and Optional versions of the Game.

Unlike many other game simulations that more experienced players may have tried in the past where movement and battle are broken down into separate steps; in SHENANDOAH movement and battle are often intermingled, with individual units being capable of moving, fighting, moving again, fighting again, etc, during the course of the Turn.

Movement in SHENANDOAH is simulated by moving the unit counters from hex to hex across the gridded mapboard. Each hex entered costs the unit being moved a portion of its Movement Allowance Factor, as does regrouping the units (Stacking and Unstacking them), changing their Formation, and engaging in Combat. A unit's Movement Allowance Factor is a numerical representation of its movement abilities, and the cost for various movements simulates the relative difficulties of these actions.

Combat in SHENANDOAH is simulated by comparing the relative strengths of the forces involved, their Formation, and the strength of their position. The often fluid nature of the Combat in the actual campaign is reflected in the Combat simulation mechanics of the Game.

\subsection{OUTLINE OF PLAY}

Each scenario in SHENANDOAH consists of a certain number of Turns. When that number of Turns is over, the game is over. Each Turn is divided into two parts; the Union Player's portion of the Turn, and the Cofederate Player's portion of the Turn, not necessarily in that order. The player who is to move first during each Turn is determined in the individual scenarios. The player who is currently in his portion, or Phase, of the the Turn is referred to as the Phasing Player, and the other player is referred to as the Non-Phasing Player. Below is a step-by-step outline of the sequence of events during a turn.

\begin{enumerate}
  \item The player whose side moves first as determined in the individual scenario is defined now as the Phasing player, and his opponent is defined as the Non-Phasing Player. The Phasing Player may now move all of his units in any direction up to the limit of their Movement Allowance Factors, within the limits and restrictions of the rules of movement. The Phasing Player should note on a scrap of scratch paper the number of Movement Allowance Factors expended by units or Stacks of units that have entered enemy Zones of Control. This information is \textit{very important} as these units in enemy Zones of Control can use any remaining Movement Allowance Factors for Combat and/or further movement.

  \item The Non-Phasing Player is now allowed to exercise his movement options, either to fall back to avoid Combat, or to stay in place and accept it.

  \item Any Combat situations are now resolved. Combat costs the Phasing Player Movement Allowance Factors, and each Combat situation continues until the Phasing Player's units use up their Movement Allowance Factors, or until the Combat is resolved to the point where the Phasing Player's units are no longer in an enemy Zone of Control.

  \item If the Phasing Player still has units with unexpended Movement Allowance Factors, he may use them for further movement and/or combat. He is allowed again to enter enemy Zones of Control, if desired, again noting on his scratch paper the current number of Movement Allowance Factors expended.

  \item Steps 2-4 are repeated until the Phasing Player has no Movement Allowance Factors left, or has no further movement he wishes to make.

  \item The player who moved first has now completed his portion of the Turn. The player moving second is now defeind to be the Phasing Player, and his opponent becomes the Non-Phasing Player. Steps 1-5 are now repeated for this player's portion of the Turn.

  \item The players now record on their Point Indicators their new point totals.

  \item The Turn Marker is advanced on the Game Turn track, signaling the completion of one Turn, and the start of another.
\end{enumerate}

\subsection{ZONES OF CONTROL}

\begin{enumerate}
  \item Infantry, Cavalry, Partisan, Artillery, and Horse Artillery units all have a Zone of Control. No other types of units in the game have Zones of Control.

  \item The six hexes that immediately surround a hex and are adjacent to it constitute the Zone of Control of any unit or units in that hex.

  \item A Zone of Control does not extend into a hex across a ridgeline.

  \item All units must stop as soon as they are moved into the Zone of Control of an enemy unit - movement can be continued only after the enemy unit has moved back (either voluntarily or involuntarily, as a result of combat) and no enemy Zones of Control cover the hex.

  \item Zones of Control do not effect combat after an initial round of combat has occurred. Enemy units in each other's Zones of Control do not necessarily have to have combat.

  \item Units may retreat into enemy Zones of Control, but only if no alternate retreat routes are available.

  \item A unit or Stack of units cannot move into an enemy Zone of Control if it lacks enough unexpended Movement Allowance Factors to engage in Combat after entering.
\end{enumerate}

(NOTE: When any of the Phasing Player's units enter an enemy zone as a result of voluntary movement they are obligated to initiate one round of combat - as explained more fully later in the rules.)

\subsection{ENTERING AND EXITING THE MAPBOARD}

\begin{enumerate}
  \item Each scenario lists the hexes where the various reinforcement units may enter the Mapboard. They may enter on those hexes, or within four hexes of the designated hex, along the same edge of the Mapboard. The player does not have to bring these units into the game; it is his choice to do so or not. The decision as to whether the units will be brought on must be made by the player ast the start of the game (exceptions: In the "long" scenarios \#6 and \#16, the player must make his decision seven Turns before the troops will arrive.); this decision to bring the troops on is indicated by placing the units to be brought on the proper Turn of their arrival on the TURN RECORD CHART.

  \item Not all reinforcement units need to be brought on; if the player wishes he may commit only part of a force, as indicated in the scenarios. Once the player decides to bring the units on, they must be placed on the Mapboard when their turn arrives, and remain for at least that Turn.

  \item Units may exit the Mapboard at certain designated hexes (see each individual scenario). Units that exit on these designated hexes are allowed to re-enter the Mapboard on a later Turn. This re-entry must be at the hex where they exited, or within four hexes of it along the same edge of the Mapboard. The decision to bring units back (again placing them in the proper box of the TURN RECORD CHART) must be made a number of Turns prior to their re-entry; that number of Turns being equal to the number of Turns since ithe units exited the Mapboard.

  \textit{For example, if on Turn Four a player decides to re-enter units that exited on Turn Two, their re-entry Turn would be Turn Six.}

  \item Units that exit the Mapboard at a hex not designated as an exit hex cannot re-enter the Mapboard, but are out of the game for good. The enemy gets no Victory Points for units driven off the Mapboard, but the player does lose their services for the rest of the game.
\end{enumerate}

\subsection{MOVEMENT BY THE PHASING PLAYER}

\subsubsection[GENERAL RULES OF MOVEMENT]{\mbox{GENERAL RULES OF MOVEMENT}}

\begin{enumerate}
  \item Dukring his portion of the Turn, the Phasing Player may move as many or as few of his units as he wishes. Each unit may be moved as many or as few hexes as desired, subject to movement restrictions and as long as the Movement Allowance Factor of a unit is not exceeded.

  \item Each unit or Stack of units is moved individually, the path of its movement being traced over the hexagonal grid while the Phasing Player announces out loud the accumulated number of Movement Allowance Factors expended by the movement in progress. The Non-Phasing Player merely observes the moves (to ensure their accuracy), and does not move any of his own units. The Phasing Player continues this until he has moved all desired units.

  \item Only units in an enemy Zone of Control have any possibility of further movement and/or Combat, so be sure to make a note of how many Movement Allowance Factors all such units have expended.
\end{enumerate}

\textit{NOTE: The Phasing Player must decide where to move a unit, then move it there while counting up the Movement Allowance Factors expended. He can retrace the movement until he what he considers to be his optimum move; but once he removes his hand from the units, he cannot later go back to change their move.}

\subsubsection{HOW TO MOVE}

\begin{enumerate}
  \item In your portion of the Turn you may move each unit up to the full expenditure of its Movement Allowance Factor.

  \item You are not obliged to move any unit in your portion of the Turn. Units are forced to move only as a result of combat.

  \item A given unit does not have to be be moved at all, or it may expend any portion of its Movement Allowance up to the maximum allowed.

  \item You may move a unit in any direction or combination of directions during your portion of the Turn.

  \item Movement Allowance Factors may not be transferred from one unit to another; and they cannot be accumulated from one Turn to the next.

  \item The die has nothing to do with movement.

  \item You must move your units during your own portion of the Turn. You may never move your units during your opponent's portion of the Turn, except as specificaly defined later in the rules. (See Non-Phasing Player Movement)
\end{enumerate}

\subsubsection{MOVEMENT RESTRICTIONS}

\begin{enumerate}
  \item Different types of terrain require the expenditure of different amounts of a unit's Movement Allowance Factor to enter.

  \item A unit must always have sufficient Movement Allowance Factors to enter a specific hex in order to do so. For instance, a unit that has expended all but one of its Movement Allowance Factors may not enter a hex requiring the expenditure of two Movement Allowance Factors.

  \item The varying cost (in Movement Allowance Factors) for various types of units to enter a hex containing specific types of terrain is shown on the MOVEMENT \& TERRAIN EFFECTS CHART.

  \item Units in Column Formation on a road are considered to be on the road and can ignore other types of terrain in the hex.

  \item Units in Column Formation can cross bridges just as if they were roads. Units in Battle Formation cannot cross bridges.

  \item Units in Column Formation that cross a river or stream hexside lose the required amount of Movement Allowance Factors for crossing the water, regardless of the type of terrain in the hex entered.

  \item Units in Battle Formation cannot cross a river or stream hex side.

  \item \textit{No} units may cross a ridge hexside at any time.

  \item In hexes where there are several types of terrain features, units in Column Formation may use the most advantageous movement rates. Units in Battle Formation always use the least advantageous movement rates.

    \textit{For example, a unit in Battle Formation in a hex with both clear and slope terrain in it will move at the cost in Movement Allowance Factors for the slope terrain, not the clear terrain.}

  \item The Valley Pike is the only macadamized (hard-surfaced) road on the mapboard. That is why it is unaffected by the muddy weather that turns other roads into quagmires.

  \item Note that railroads play no part in the Basic Game - ignore them for purposes of identifying terrain.

  \item The road network on the Mapboard is laid out to cut through many different hexes to represent the winding nature of the actual roads. The path of the roads must be followed to use road movement costs. Moving from one hex containing a road to another hex, also containing a road, but not along the path of the road in the first hex is \textit{not} road movement.
\end{enumerate}

\subsection[MORE THAN ONE UNIT PER HEX]{\mbox{MORE THAN ONE UNIT PER HEX}}

\begin{enumerate}
  \item Up to thirty Stacking Factors may be present in any one hex at any one time. This limit can never be exceeded, even if units must be eliminated from the game to avoid exceeding it.

  \item Each type of unit counter has a specific Stacking Factor (as listed on the MOVEMENT \& TERRAIN EFFECTS CHART). Any combination of units may be placed together in a hex, as long as their combined Stacking Factor does not exceed thirty.

  \item A unit counter or Stack of units cannot be moved into a hex containing other friendly units without Stacking them together. A unit counter or Stack of units cannot be moved out of a hex containing other friendly units without Unstacking them. Movement Allowance Factors are always expended when any Stacking or Unstacking takes place in a hex.

  \item In no case may units be Stacked with enemy units in the same hex.

  \item Unit counters with various Combat Factors are provided for the player's convenience, to avoid large Stacks when strong forces are present in one hex. Large Combat Factor units can replace a number of smaller Combat Factor units of the same type, or vice-versa, at any time a player wishes to do so, as long as the number of Combat Factors remains the same. In other words, treat the counters as if they were "change" - i.e. five pennies (five "1" Combat Factor unit counters) equals one nickel (one "5" Combat Factor unit counter).
\end{enumerate}

\textbf{Example of Play \#1: Movement Restrictions}

Note the cost to enter various hexes, depending on the terrain in the hex, and the Formation of the unit. Unit 2-6 (in Column Formation) crosses the bridge and follows the road (the path of the road must be followed exactly for the unit to use road movement costs), then crosses a stream hexside (expenditure of 2 MAF, regardless of the type of terrain in the hex), finishing its movement over clear terrain (total 6 MAF expended). Unit 1-6 (in Column Formation) crosses the river hexside (expenditure of 3 MAF, regardless of the type of terrain in the hex), then finishes its movement over slope terrain (total 6 MAF expended) - note that it could not have crossed over the ridge hexsides. Unit 5-6 (in Battle Formation) moves into two hexes containing slope terrain (expending 3 MAF per hex entered, total 6 MAF expended) - not that it could not cross the stream hexside, as it is in Battle Formation.

TODO: Insert image here.

\textbf{Example of Play \#2: Stacking Factors}

The Stack of thrity Infantry Combat Factors does not exceed the limits for their hex, as Infantry Combat Factors count for only one Stacking Factor each. The Stack of fifteen Artillery counters is illegal, because Artillery Combat Factors count for three Stacking Factors each. Thus, the Artillery Stack exceeds the limit by fifteen Stacking Factors - no more than ten Artillery Combat Factors could ever be in one hex.

TODO: Insert image here.

\subsubsection[STACKING \& UNSTACKING UNITS]{\mbox{STACKING \& UNSTACKING UNITS}}

\begin{enumerate}
  \item The placing of units in a stack with other units in the same hex, or taking a unit or units from a hex where it was previously stacked with other units represents a reorganization of the units in the hex, some marching and counter-marching, etc, all of which takes time and costs Movement Allowance Factors.

  \item Stacking or Unstacking a unit or units costs a varying number of Movement Allowance Factors for \textit{all} units in the hex, depending on the terrain in the hex in which it is done. These costs are shown on the MOVEMENT \& TERRAIN EFFECTS CHART.

  \item In hexes where there are several types of terrain features, the highest cost is the one used.

    \textit{For example, a unit in a hex that contains both clear and slope terrain will use up the number of Movement Allowance Factors appropriate for slope terrain when Stacking and Unstacking units.}

  \item Roads are ignored as terrain for the process of Stacking and Unstacking units.

  \item Stacking of units may be done at any time during a Player's turn, provided that each involved unit has enough Movement Allowance Factors left to do so. Similarly, units may be Unstacked at any time during a players Turn, provided that each involved unit has enough remaining Movement Allowance Factors to do so.

  \item Once stacked together, the units in the hex may continue to move together as if they were all one unit. They cannot split up until Movement Allowance Factors are used to Unstack them.

  \item All units in the same hex must be Stack together - there cannot be several different Stacks in the same hex.
\end{enumerate}

\textbf{Example of Play \#3: Stacking \& Unstacking}

TODO: Insert image here.

Note that the Cavalry unit expends 2 MAF to Unstack from the 9-6 unit since this is a slope hex. The Cavalry unit must expend 1 MAF to stack with the 6-6, then expend 1 MAF to Unstack with it, in order to move through the hex that the 6-6 occupies. A total of 9 MAF are expended by the Cavalry unit for this move. Note that Infantry units in this example were also required to expend MAF for Stacking and Unstacking.

\subsubsection{STACKING COUNTERS AND STACKING BOXES}

\begin{enumerate}
  \item A large Stack of many unit counters in the same hex is awkward to move, and difficult for a player to handle. For this reason, the Stacking Counters and Stacking Boxes are provided (the Stacking Boxes also have a purpose for Combat, explained later in the rules).

  \item Each Stacking Counter is identified by a letter, and for each Stacking Counter there is also a Stacking Box printed on the Mapboard that has a corresponding letter (there are also Stacking Boxes without an identifying letter, whose use is explained later in the rules).

  \item For convenience, players may at any time remove a Stack of unit counters from a hex on the Mapboard. A Stacking Counter is then placed in that hex, and the unit counters are placed in the Stacking Box with the letter corresponding to the letter on the Stacking Counter. The Stacking Counter now represents that Stack of units on the Mapboard hex, and the player can spread out his units in the Stacking Box for greater ease of play and/or Combat purposes.
\end{enumerate}

\subsubsection{FORMATIONS}

\begin{enumerate}
  \item The Formation a unit or stack of units is in plays a very important role in the game. In Column Formation, units are deployed for rapid marching and manuevering, but are not efficient for combat. In Battle Formation, units are deployed for maximum effectiveness in combat, but are not efficient for rapid movement.

  \item Changing the formation a unit counter is in from Column Formation to Battle Formation or back again costs a varying number of Movement Allowance Factors, depending on the type of unit and the terrain in the hex in which the Formation change takes place. These costs are shown on the MOVEMENT \& TERRAIN EFFECTS CHART.

  \item In hexes where there are several types of terrain features, the highest cost is the one used.

  \textit{For example, a unit in a hex containing both clear and slope terrain will use up the number of Movement Allowance Factors appropriate for slope terrain when changing Formation.}

  \item Roads are ignored as terrain for the process of changing Formation.

  \item A player may change the Formation his units are in at any time during his Turn, provided that the units have enough remaining Movement Allowance Factors to do so.

  \item It is possible for some units in a hex to be in Column Formation, while other units in the same hex are in Battle Formation. Note that such a situation will cause some varying movement costs through the same hex. Even though in different Formations, all units in the same hex must be stacked together.

  It is possible for the Phasing Player to change Formation while in an enemy Zone of Control. This must be done prior to beginning the first Round of Combat.
\end{enumerate}

\subsubsection{MARKING FORMATIONS}

\begin{enumerate}
  \item Units in Column Foramtion are indicated by placing a Column Formation Marker on top of a unit or Stack of units in that Formation.

  \item Units in Battle Formation are indicated by \textit{not} having a Column Formation marker placed on top of them, i.e. any units that do not have a Column Formation Marker placed on top of them are in Battle Formation.

  \item For hexes containing units in both Formations, indicate by placing Column Formation Marker on top of them. Then place the units in Battle Formation at the top of the Stack, on top of the Column Formation Marker.
\end{enumerate}

\subsubsection{NON-PHASING PLAYER MOVEMENT}

\begin{enumerate}
  \item Normally, the Non-Phasing Player cannot move his units, but must sit and watch the Phasing Player move his. However, the Non-Phasing Player is allowed to move his units that are to be withdrawn \textit{one} hex.

  \item The Non-Phasing Player must be in Column Formation in order to withdraw a hex. He is allowed to change his Formation from Battle Formation to Column Formation in order to withdraw.

  \item A withdrawal is not allowed into a hex that is in the Zone of Control of an enemy unit whose Zone of Control it is already in. However, if no other alternative exists a unit may withdraw into the Zone of Control of an enemy unit to which it was not previously adjacent.

  \item A Stack cannot Unstack and withdraw into two or more different hexes. All withdrawals must be from one hex into another hex with all units included.

  \item A withdrawal may be made into any hex (subject to the above limitations, and not over Prohibited hex sides), without regard to how many Movement Allowance Factors would be expended.

  \item Units may withdraw into a hex containing other friendly units and be Stacked with them, as long as the Stacking Limits are observed.
\end{enumerate}
