\section{COMPONENTS}

\subsection{MAPBOARD}

The Mapboard shows the parts of Virginia and West Virginia in and immediately adjacent to the Shenandoah Valley in which important Civil War campaigns took place in 1862 and 1864. A hexagonal grid has been superimposed on the map to facilitate movement. Each individual hexagon is referred to as a "hex". Terrain has been somewhat simplified and, in some cases, slightly reconfigured to conform to the hexagon grid-coordinates to help pinpoint locations.

\textit{For example: Winchester is N-20, Luray is S-36, Charlottesville is BB-53, and so on.}

Partial hexes along the side of the map with 3 sides can be used for play; all other partial hexes are considered to be "off the board" and cannot be used for play.

The Mapboard also includes other features to aid in the play of SHENANDOAH. Victory Points for boths sides are tabulated on the POINT RECORD. The TURN RECORD CHART is used to keep track of the time. Two sets of Stacking Boxes are also included, one set for each player.

An arrow on the Mapboard (near the logo) shows the direction that is true North. However, for game purposes, the directions are defined differently for simplicity. North is considered to be that edge of the Mapboard that contains the grid coordinate numbers. West is the edge containing the grid coordinate numbers 1-44. South is the edge containing grid coordinate numbers 45-58. East is the remaining edge of the Mapboard.

\subsection{UNIT COUNTERS}

Contrasting colored die-cut counters are provided for the play of SHENANDOAH. These are your playing pieces for the game, and will henceforth be known as unit counters, or units, for short. They represent the various units available to the opposing armies in the campaign.

The blue units with with printing represent the Union forces; the Confederate forces are represented by gray units with red printing; the tan units with red printing may be used by both sides. These units need to be punched from the die-cut sheet for use, and it will be to your advantage to keep the units separated by color and type once punched out, as this greatly facilitates setting up the game. The opposing forces in each of the varying Orders of Battle (in the various scenarios) are composed by selecting units from the those provided. The units are distinguished by type, strength, and mobility, as represented by various numbers and symbols printed on their faces.

TODO: Insert images here.

\subsection{PREPARATION FOR PLAY}

\begin{enumerate}
  \item The Mapboard should be placed on a smooth level surface. The Union player sits at the northern edge of the Mapboard, and the Confederate player sits at the southern edge of the Mapboard.
  \item Players should now lay out the Play-Aid Units where indicated on the Mapboard; that is, the Stacking Counters, Point Marking Counters, and the Turn Marking Counter.
  \item Players should now place other auxiliary units in handy locations; these being the Column Formation Markers, and any extra Supply, Fortification, and Destruction Counters not in the game at the Start.
  \item Players should now decide what scenario is to be played, what rules should be used (Basic, Advanced or Optional), etc. Units should be selected to compose the forces listed in the scenario, and set on the Mapboard where indicated.
  \item Spare units should be sorted and placed in some convenient location for later introduction into the game.
\end{enumerate}

\subsection[GAME EQUIPMENT INVENTORY]{\mbox{GAME EQUIPMENT INVENTORY}}

\begin{itemize}
  \setlength{\itemsep}{-0.7em}
  \item One Rules Folder
  \item One Set Unit Counters (374)
  \item One Game Mapboard
  \item One Sheet of Charts
  \item One Screen
  \item Two Counter Storage Trays
  \item One Box
\end{itemize}

\subsection{GAME SCALE}

The Game scale is two and one-half miles to the hex, and one Turn represents one day of actual time. A Combat Factor represents from 200 to 500 actual men, or from 3 to 8 actual artillery pieces.

The actual number of men and guns that one Combat Factor represents varies so widely due to the great differences in experience, training, leadership, and morale of various real Civil War formations. For instance, a force of 200 veteran troops under experienced officers and NCO's would be more than a match for a force of 500 green or militia troops - thus, a Combat Factor is more of a representation of combat effectiveness than of actual head counts.)
