\section{INTRODUCTION}

SHENANDOAH is a game of tactical simulation. It represents the results of a long an extensive research effort to accumulate facts and data to simulate conditions as they were at the tiem the actual events were taking place.

Simulations come in many different forms. A scene staged and shot for a movie is a "visual" simulation of reality. A scene described in a book can be regarded as a "written" simulation. Similarly, the Mapboard, counters, rules, etc, contained in this box constitute a "gaming" simulation of "the real thing". Absolute realism in any type of simulation is, of course, impossible; but, within the framework of this game, the major factors and problems confronting the actual antagonists in the historical campaign are simulated. Through the use of this game, players can gain an appreciation of "how it really was", and of the factors that influenced the actual commanders in their actions. However, unlike visual or written simulations, the game player does not merely take a passive role in watching or reading the simulation, but becomes an active participant in it. The players take the roles of the opposing commanders - \textit{they} are in command, and it is \textit{their} decisions and \textit{their} actions that will determine the result.

SHENANDOAH is basically a two-player game. Players move their units and execute their attacks on enemy units in turn, while attempting to fulfill the Victory Conditions. To move from hex to hex, each unit expends a portion of its Movement Allowance Factor. Combat also requires the expenditure of Movement Allowance Factors, and is resolved by each player rolling the die.

The rules for SHENANDOAH are divided into three sections. The first section is called the Basic Game, and contains all the rules needed to play a simple, uncomplicated version of the Game. The second section of the rules is the Advanced Game, a more complex and realistic set of rules than the Basic Game. The third section, the Optional Game, builds in further complexity and realism for players who prefer their games that way.