\subsection{RAIL MOVEMENT}

Rail movement was the fastest and easiest method of transportation available during the American Civil War. On the Mapboard, only two rail lines are operable, the Baltimore \& Ohio (B\&O RR) and the Virginia Central (Va. Cent. RR); all other lines were too torn up to be of any use, and are included on the Mapboard for historical interest only. The B\&O RR is the line running from hex A-11, through Bath, Martinsburg, Harper's Ferry, to Hex Z-13. It can only be used for rail movements by the Union Player. The Va. Cent. RR is the line running from Hex L-50, through Staunton, Waynesboro, Charlottesville, to Hex CC-53. It can only be used for rail movements by the Confederate Player.

\begin{enumerate}[label=(\alph*)]
  \item Units being moved by rail may move any distance along the path of the rails without using any Movement Allowance Factors (i.e. the movement is "free"). They may not move through destroyed rail hexes in this manner, nor may they move through a hex occupied by enemy units, or through a hex in an enemy's Zone of Control.

  \item Units being moved by rail may move through a hex occupied by other friendly units without the need to Stack or Unstack with them, unless the other friendly units are also loaded to use rail movement.

  \item Units must be in Column Formation to be loaded on a train. It costs Movement Allowance Factors to load and unload a unit from a train (see MOVEMENT AND TERRAIN EFFECTS CHART).

  \item Supply counters can be moved by rail. They not not get loaded or unloaded, but can be placed on the rails by Unstacking with a Wagon counter in a rail hex, or can be taken off the rails by Stacking with a Wagon counter. For rail movement only, a Supply counter has 10 Stacking Factors.

  \item There are no "train" counters in the game. Instead, they are simulated by units expending Movement Allowance Factors to "load" and "unload" while on a rail line. As there is not an infinite number of "trains" available, there are limits to the carrying capacity of both active rail lines on the Mapboard. Rail movement cannot be used by over thirty Stacking Factors per Turn on the B\&O RR. The capacity of the Va. Cent. RR is twenty Stacking Factors per Turn.

  \item Units moving by rail follow the path of the rail lines, and can ignore all other terrain in the hexes they move through.
\end{enumerate}