\rulesection{13.0 Demoralization}

At the end of the combat round in which a force's losses first total 10\% or more of the initial committed strength, and every subsequent round, that player checks for demoralization with a single die roll for all participating units in the hex.

\rulesubsection{13.1 Procedure}

Roll one die and add the following modifiers:
\begin{itemize}
\item +1 for every 10\% of the initial committed force lost, ignoring fractions.
\item +1 if the senior leader has a command rating of 4.
\item -1 if the highest-ranking leader has a command rating of 1.
\item -1 for the defender if any units in his force are entrenched.
\item +1 if any units begin the battle demoralized.
\end{itemize}

If the modified die roll is 6 or more, all participating friendly combat units in the hex immediately become demoralized. Units in the same hex but not taking part are unaffected.

\rulesubsection{13.2 Effects}

If a force fails a demoralization check, all participating friendly units in the hex must immediately retreat. If a force includes demoralized units at the start of battle, it retreats only when it fails a check during that battle.

\textbf{13.21} Demoralized units may not attack.

\textbf{13.22} If any defending units are demoralized, the defender subtracts 1 from his commitment die roll and may not choose \textit{Pitched Battle}.

\textbf{13.23} If any units begin combat demoralized, the owning player adds 1 to all demoralization die rolls.

\textbf{13.24} Demoralization does not affect reaction.

\textbf{13.25} There is no additional penalty if a demoralized unit becomes demoralized again.

\rulesubsection{13.3 Recovery}

During the Morale Recovery Phase each player attempts to restore demoralized units, including those demoralized in the same turn.

\textbf{13.31} Add 1 to the leader's initiative and roll one die. If the result is equal to or less than the modified initiative, the unit returns to good order.

\textbf{13.32} If a supreme commander is stacked with a demoralized unit, the player may use the supreme commander's initiative instead of the demoralized leader's. A cavalry commander may give this benefit only to cavalry units.
