\rulesection{16.0 Destruction and Repair}

\rulesubsection{16.1 Destroying Bridges}

A force totaling five or more SPs may destroy a bridged hexside by expending MPs in an adjoining hex:
\begin{itemize}
\item 4 MPs to destroy a rail bridge;
\item 3 MPs to destroy any other bridge;
\item +2 MPs to either cost if an enemy combat unit occupies a hex adjoining the bridge.
\end{itemize}

Before a bridge is destroyed, enemy combat units may attempt reaction and, if successful, may enter the hex of the unit attempting the destruction. If this occurs, the bridge may not be destroyed.

\textbf{16.12} Place a Bridge Destroyed marker on the destroyed hexside. If a rail bridge is destroyed, also place a Destroyed Rail marker in the hex occupied by the destroying unit.

\textbf{16.13} Units may not destroy bridges during force march or if stacked with an enemy combat unit.

\rulesubsection{16.2 Repairing Bridges}

A force totaling five or more infantry SPs may repair a bridge. Cavalry may not repair bridges.

Repair requires one full friendly Movement Phase. During that phase the unit must remain adjacent to the hexside, no enemy unit may be adjacent to it, the unit may not move, and it must have at least 1 CP. At the end of the phase remove the Bridge Destroyed marker.

Repairing a rail bridge does not remove the Destroyed Rail marker placed when the bridge was destroyed; that must be repaired separately after the bridge is repaired. Players may not build new bridges, only repair printed bridges that have been destroyed.

\rulesubsection{16.3 Destroying Rail Lines}

A force totaling five or more infantry SPs may destroy a rail line by expending 3 additional MPs in the hex. Place a Destroyed Rail marker. Rails may not be destroyed if enemy units are in the hex.

\rulesubsection{16.4 Repairing Rail Lines}

A force totaling five or more infantry SPs may repair a friendly rail hex by expending 4 additional MPs in the hex and removing the Destroyed Rail marker.

\textbf{16.41} Rail lines may not be repaired if enemy units are in the hex.

\textbf{16.42} The same unit may not simultaneously repair rail lines and a bridge.

\textbf{16.43} Only lines in friendly territory, meaning lines the player's units could use for rail movement, can be repaired.

\textbf{16.44} Cavalry may not repair rail lines.
