\rulesection{5.0 Leaders}

Leaders are the heart of the system. To reflect individual qualities, leaders have four ratings:

\begin{itemize}
\item \textbf{Command rating} determines movement allowance together with command points.
\item \textbf{Initiative} affects morale recovery, forced march, reaction movement, and the ability to leave enemy-occupied hexes.
\item \textbf{Combat bonus} modifies combat die rolls.
\item \textbf{Seniority rating} determines which leader's ratings are used when several are stacked together.
\end{itemize}

\rulesubsection{5.1 Supreme Commanders}

Supreme commanders are fundamental because command points originate with them. Supreme commanders are:

\begin{itemize}
\item Union: Banks, Fremont, and Shields in the 1862 scenarios; Sigel in scenarios 4 and 5; Sheridan in scenario 6.
\item Confederate: Jackson in all 1862 scenarios and Early in all 1864 scenarios except 5, where Breckenridge is supreme commander.
\end{itemize}

Supreme commanders broadcast CPs to other friendly leaders.

\rulesubsection{5.2 Subordination}

Certain leaders are subordinate to others, reflecting each army's organization. The Player Record Sheets list which leaders are subordinate to which others in each scenario. Subordination is indicated by color bands on the counters.

\textbf{5.21} All units are subordinate to the supreme commander.

\textbf{5.22} All cavalry units are subordinate to the cavalry commander, who is used to control cavalry at long distances from the supreme commander. Some cavalry are also subordinate to intermediate commanders as indicated by color bands. In addition, Union cavalry are subordinate to all army leaders.

\textbf{5.23} All wagons are subordinate to all friendly leaders.

\rulesubsection{5.3 Seniority}

Each leader has a seniority rating. The leader rated 1 is senior, the leader rated 2 is next, and so on. Seniority determines which leader is in overall control when several are stacked together. A commander may control leaders who do not belong to his formation if he is the senior leader in the hex. Subordination does not affect seniority.
