\rulesection{7.0 Movement}

During a player's Movement Phase, he may move every unit whose movement allowance is greater than 0. Units may be moved singly or in stacks. Each expends movement points (MPs) to enter hexes depending on terrain.

\rulesubsection{7.1 Terrain}

The Movement Costs Chart lists the cost for each type of unit to enter each type of terrain or cross certain hexsides. A combat unit may not enter a hex if it cannot pay the full MP cost.

\textbf{7.11} Units entering a hex through a road hexside may use road movement rates. A road negates slope costs but not ford costs.

\textbf{7.12} Every rail line is also considered a road.

\textbf{7.13} If two roads run parallel in a hex but do not connect, a unit may not enter on one and leave on the other in the same turn using road movement; it pays the full terrain cost for the second hex.

\textbf{7.14} Units pay an additional cost to move in either direction across a slope hexside.

\rulesubsection{7.2 Stacks}

A stack of more than one unit moving together is called a force. If a stack of more than one type of unit moves together, each unit's movement allowance may be reduced. During the move, each unit pays the costs for its own type. Forces may not split up during movement or drop off units; units moving as a force must finish together.

\rulesubsection{7.3 Modifications}

Combat unit movement allowances are modified when units move together as stacks or when units leave a hex separately. This applies in both regular Movement Phases and Reaction Movement.

\textbf{7.31} When more than two divisions move together as a force, reduce the force's movement allowance by 1 MP for each division after the second.

\textbf{7.32} Every 25 or more SPs of cavalry or infantry detachments is treated as one division.

\textbf{7.33} If units that begin stacked together move out separately, a combat unit loses 1 MP for each division already moved. Detachments and cavalry do not count for this purpose. There is no cost for enemy units. A wagon's movement allowance is never reduced for units that have left the hex.

\textbf{7.34} Stacking can never reduce a unit's movement allowance to 0; it always retains 1 MP.

\textbf{7.35} Stacking does not affect movement allowances of wagons or commanders.

\rulesubsection{7.4 Enemy-Occupied Hexes}

Units may enter enemy-occupied hexes and must do so in order to attack.

\textbf{7.41} A unit must expend 1 additional MP to enter a hex occupied by an enemy combat unit, and may not expend any more MPs that Movement Phase. There is no additional cost to enter a hex occupied only by a non-combat unit.

\textbf{7.42 Reaction.} If an enemy unit moves into a friendly unit's hex, the friendly unit may immediately attempt to leave through reaction. If an enemy combat unit using reaction movement enters the hex of a moving friendly unit, neither unit may expend more MPs in that Movement Phase.

\textbf{7.43 Exiting Enemy-Occupied Hexes.} A unit beginning movement or reaction in a hex occupied by enemy combat units may attempt to leave. Roll one die and compare the initiative ratings of the senior friendly and enemy leaders. Add 1 if the enemy leader's initiative exceeds the friendly leader's; subtract 1 if it is lower. If the modified die roll is equal to or less than the senior moving leader's initiative, the force may leave, paying 1 additional MP. If the result exceeds the initiative rating, movement immediately ends. Before rolling, the player must declare exactly which units are attempting to leave.

\textbf{7.44 Non-Combat Units.} If a commander or wagon occupies a hex with no friendly combat units, enemy combat units may enter at no additional movement cost. The friendly unit is eliminated. An unaccompanied commander or wagon may not enter a hex containing an enemy unit.

\rulesubsection{7.5 Force March}

Any unit entitled to use all of its printed movement allowance may force march if the senior leader in the stack received CPs equal to his command rating. Each unit may expend additional MPs equal to the senior leader's initiative. No die roll is required.

\textbf{7.51} A unit may not force march and destroy things in the same Movement Phase.

\textbf{7.52} Units that force march may lose SPs. Immediately after moving, roll one die. On 1--4, no SPs are lost. On 5 or 6, 10\% of the unit's strength is eliminated, rounding up.
