\rulesection{10.0 Railroad Movement}

Both players may move units by rail using friendly rail only. The Union may use rail starting at hex 1005 and ending at hexes 1601, 1901, and 2901. The Confederate player may use rail starting at hex 1043 and ending at hexes 1853, 4653, and 4831.

\rulesubsection{10.1 Procedure}

The unit must move to a rail hex and expend 1 MP to entrain. Place an Entrained marker on the unit. The unit then expends 1 MP for every 15 hexes it wishes to move by rail. It may detrain for 1 MP and then spend any remaining MPs on normal movement. If it does not detrain, the player may place a Destination marker.

\rulesubsection{10.2 Restrictions}

\textbf{10.21} A unit may remain entrained at the end of the Movement Phase and use rail movement again in the next phase without entraining again.

\textbf{10.22} In a single Movement Phase a unit may move as many hexes by rail as its movement allowance permits.

\textbf{10.23} A unit may not use rail movement during reaction. An entrained unit may not react.

\textbf{10.24} An entrained unit does not pay additional MPs to enter an enemy-occupied hex or ZOC. It must stop upon entering an enemy-occupied hex and may detrain if it has at least 1 MP remaining.

\textbf{10.25} An entrained unit must stop upon entering a hex with a destroyed rail marker.

\textbf{10.26} An entrained unit must stop upon entering a hex containing an enemy non-combat unit. Unlike regular movement, this does not automatically eliminate that non-combat unit unless the entrained unit detrains.

\rulesubsection{10.3 Rail Capacity}

In a single Movement Phase a player may move any two divisions, detachments, or wagons by rail. Supreme and cavalry commanders may also move by rail in addition to those units. A unit that begins the phase entrained but does not move by rail does not count against capacity.

\rulesubsection{10.4 Destination Markers}

If the player leaves a unit entrained at the end of the Movement Phase, he may place a Destination marker. In the next friendly Movement Phase, the entrained unit may continue toward its destination without receiving a CP. It may move up to 60 hexes, equivalent to 4 MPs worth, per turn. The unit must move toward the destination by the most direct route. If the player wishes to move the unit differently, the unit must have a CP and the Destination marker is removed.

\rulesubsection{10.5 Combat Effects}

An entrained unit may not attack. If attacked, it immediately detrains. The owning player subtracts 1 from his commitment die roll if any such unit is involved.
