\rulesection{14.0 Retreats}

\rulesubsection{14.1 Required Retreats}

Units must retreat:
\begin{itemize}
\item immediately when demoralized;
\item at the end of combat if unsupplied, unless the enemy retreats because of demoralization;
\item at the end of combat if the player chose \textit{Withdrawal}.
\end{itemize}

Units in the same hex but not participating in the combat need not retreat. If both sides retreat, the player whose senior leader has the greater command rating retreats first; if equal, the attacker retreats first.

\rulesubsection{14.2 Procedure}

A player retreats his own units on any path he wishes, subject to restrictions. Different units may retreat to different hexes.

\textbf{14.21} Retreating units move 4 MPs without paying ZOC costs. If no path exactly 4 MPs long is available, they may expend more, but as few extra MPs as possible.

\textbf{14.22} A unit that must retreat but has no legal route at least 4 MPs long is removed from play.

\rulesubsection{14.3 Enemy Units}

With one exception, retreating units may not enter hexes occupied by enemy combat units, nor exit the combat hex by a hexside through which enemy units entered the battle unless those enemy units retreated first.

Exception: enemy units totaling less than 20\% of the strength of the retreating force do not block retreat. At a bridge hexside, enemy units totaling at least 10\% block retreat. Units may retreat through any enemy-occupied hex only if there is no alternative.

\rulesubsection{14.4 Other Restrictions}

\textbf{14.41} Retreating units may not cross unbridged river hexsides.

\textbf{14.42} A unit retreating because of demoralization must end in a hex from which it can trace a shorter supply line than from the combat hex, if possible. If not, it must retreat to a hex closer to another friendly force than the combat hex, if possible.

\textbf{14.43} Units retreating because of supply or \textit{Withdrawal} must retreat to a hex that is closer to another friendly force than the combat hex, if possible.

\rulesubsection{14.5 Wagons}

Wagons stacked with a retreating force may accompany that force for the full length of its retreat, ignoring wagon terrain costs. Likewise, any wagon in a hex a force retreats through may accompany that force.
