\rulesection{3.0 Sequence of Play}

In each turn, both players move and attempt to react to enemy movement. Then all battles are resolved in one Combat Phase.

\textbf{I. Initial Phase}
\begin{itemize}
\item Reinforcements: each player checks for reinforcements entering this turn.
\item Replacements: each player rolls for replacements. There are no replacements on turn 1 of any scenario.
\item Wagon Creation: each player may attempt to create wagons.
\end{itemize}

\textbf{II. Initiative Phase} Initiative for the turn is determined.

\textbf{III. First Command Phase}
\begin{itemize}
\item The first player determines available command points.
\item The first player may broadcast command points.
\end{itemize}

\textbf{IV. First Movement Phase}
\begin{itemize}
\item The first player moves his units and receives reinforcements.
\item The second player may attempt reaction.
\item The first player's units may destroy or repair bridges or rail hexes, and may entrench.
\end{itemize}

\textbf{V. Second Command Phase} Same as the first, with the second player receiving and broadcasting command points.

\textbf{VI. Second Movement Phase} Same as the first, with the second player moving and the first player attempting reaction.

\textbf{VII. Combat Phase}
\begin{itemize}
\item Combat: opposing units in the same hex resolve combat.
\item Depletion: check for wagon depletion.
\end{itemize}

\textbf{VIII. Conclusion Phase}
\begin{itemize}
\item Morale Recovery: players may attempt to remove demoralization.
\item Replenishment: eligible wagons are flipped to their undepleted sides.
\item Union Panic Track: in 1862 scenarios only, the track is adjusted and results applied.
\end{itemize}
