\rulesection{11.0 Supply}

Units must be supplied to function normally during combat. Supply has no effect on any other game function. There are three types of supply sources: wagons, supply bases, and depots.

\rulesubsection{11.1 Depots}

Depots are listed for each scenario. See the specific scenario on the player record sheets.

\textbf{11.12 Enemy Units.} If an enemy combat unit occupies a depot hex, friendly units not in that hex may not use it for supply or line of communications. Friendly units in the hex may use it normally. If the town holding the depot is devastated, the depot is permanently destroyed and its marker is removed.

\rulesubsection{11.2 Wagons}

Wagons carry a limited amount of supply and may become depleted due to combat. Depleted wagons have the same command, initiative, and combat bonus ratings as undepleted wagons.

\textbf{11.21 Wagon Creation.} Leaders, including detachments, may create wagons. The leader must spend one full Movement Phase in a depot or base hex, must not move during that phase, and must have at least 1 CP. Place a Wagon Creation marker in the hex. During the Initial Phase of the following turn the player may place a wagon in the hex. If all friendly wagons are already in play, no more can be created.

\textbf{11.22 Replenishing a Wagon.} To become undepleted, a wagon must remain stationary for one full turn on a road or rail hex and within four undestroyed rail and-or road hexes of a friendly depot or base. Only friendly rail hexes may be used. The four-hex path cannot be traced through enemy combat units; ZOCs have no effect. The wagon is flipped to its undepleted side during the Conclusion Phase.

\rulesubsection{11.3 Supply Base}

A supply base functions like a supply depot except that it can move. To move a supply base, flip it to its blank side during the Movement Phase and move it as a wagon. It may be flipped back to its base side at the beginning of any Movement Phase. While moving, it may not supply any units.
