\rulesection{8.0 Zones of Control}

Cavalry units only have a zone of control (ZOC), except when in a hex occupied by an enemy combat unit or when entrenched. All enemy units must pay 1 additional MP to enter a ZOC. The hexes a unit controls depend on its facing.

\rulesubsection{8.1 Union Cavalry ZOCs --- 1862 Scenarios}

Each Union cavalry unit exerts a ZOC into its three adjacent frontal hexes. All enemy units must pay 1 additional MP to enter a controlled hex.

\rulesubsection{8.2 Confederate Cavalry ZOCs and Union Cavalry in 1864 Scenarios}

Each 1864 Union and each Confederate cavalry unit's ZOC extends a distance of two hexes through its frontal hexsides. ZOCs extend into, but not through, hexes occupied by enemy combat units. Non-combat units do not block ZOCs. Units must pay 2 additional MPs to enter a cavalry unit's frontal hex and 1 additional MP to enter a ZOC hex two hexes away.

\rulesubsection{8.3 Facing}

Cavalry are the only units with facings. Each cavalry unit has three front hexsides, called frontal hexes. A player decides a unit's facing when he moves it into a hex, before the enemy declares reaction attempts. After a battle, including retreats, each player may orient the facings of involved cavalry however he wishes.

\rulesubsection{8.4 Limits}

If an enemy combat unit occupies its hex, a cavalry unit does not exert a ZOC. The ZOC disappears at the instant the enemy enters the hex and reappears when no enemy is present. ZOCs do not extend across rivers except at intact bridge hexsides, or into ridge hexes. Cavalry in entrenchments do not have ZOCs. Opposing ZOCs do not neutralize each other.

\rulesubsection{8.5 Effects}

A unit need not stop on entering an enemy ZOC, but must pay the additional MP cost for every such hex entered. A unit may move directly from one ZOC to another. ZOC costs are not cumulative: if more than one unit exerts a ZOC, use the greatest cost that applies.

A friendly combat unit negates an enemy ZOC in that hex for purposes of command broadcast, but not for movement.
