\documentclass[11pt]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}

\definecolor{titleline}{RGB}{131,44,39}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.25em,topsep=0.25em}
\setlist[enumerate]{leftmargin=1.4em,itemsep=0.35em,topsep=0.35em}

\begin{document}

{\LARGE\bfseries Scenario 3 Example of Play\par}
{\large Harper's Ferry to Port Republic, Turns 5 and 6\par}
\vspace{0.25em}
\color{titleline}\rule{\textwidth}{1.2pt}\par
\vspace{0.45em}

This example drops into Scenario 3 near its historical climax, after Jackson has already withdrawn south and the Union columns have spent several turns in pursuit. It is intended to show command, movement, reaction, combat, retreat, and morale recovery in the final phase of the campaign. The die rolls are chosen for teaching purposes and to produce a historically plausible result.

\textbf{Assumed position at the start of Turn 5.}

\begin{itemize}
\item Jackson, Winder, and the Confederate wagon are near Port Republic, prepared to face Shields.
\item Ewell and Ashby are west of the main Confederate body, positioned to delay Fremont in a Cross Keys-style holding action.
\item Fremont is approaching from the west; Shields is approaching from the east; Banks is too far away to matter directly in the coming battles.
\item The Confederate player wants to keep Fremont busy on Turn 5, then mass against Shields on Turn 6.
\item Scenario 3 is a 1862 scenario, so the Confederate player has the initiative on a die roll of 1--5.
\end{itemize}

\textbf{Turn 5. Holding action west of the river}

\textbf{1. Initial Phase}

There are no reinforcements or replacements in this scenario, so the phase ends immediately.

\textbf{2. Initiative Phase}

The Confederate player rolls a \texttt{4}. In a 1862 scenario that gives the Confederates the initiative, so they move first.

\textbf{3. Confederate Command Phase}

Jackson is still the only Confederate supreme commander, so only one command-point die roll is needed. The Confederate player rolls a \texttt{4}, receiving \texttt{2} CPs. That is enough to keep the army moving, but not enough for the whole command to act with maximum freedom.

For purposes of this example, Ewell's stack receives enough command through the chain of command to take up and hold the desired blocking position, while Jackson and Winder retain enough movement to stay concentrated near Port Republic.

\textbf{4. Confederate Movement Phase}

The Confederate player uses the turn to divide roles clearly:

\begin{itemize}
\item Ewell and Ashby move into a strong blocking position on the western approach, where Fremont must attack or lose time.
\item Jackson, Winder, and the wagon remain east of the main blocking action, preserving supply and preparing for a decisive attack against Shields on the next turn.
\item The Confederate player avoids overextending the wagon. It remains close enough to support battle but does not enter an exposed front-line hex.
\end{itemize}

No force march is required here. The Confederate object is economy and delay, not a desperate lunge.

\textbf{5. Union Command Phase}

The Union has three supreme commanders in the 1862 scenarios, so Fremont and Shields each determine their command separately; Banks's roll is irrelevant to the decisive action and is omitted from the example.

\begin{itemize}
\item Fremont rolls a \texttt{5} and receives \texttt{3} CPs. With a command rating of \texttt{4}, that gives him \texttt{75\%} movement allowance: infantry and leaders have \texttt{6} MPs, cavalry has \texttt{8} MPs.
\item Shields rolls a \texttt{3} and receives \texttt{2} CPs. With a command rating of \texttt{3}, that gives him about \texttt{66\%} movement allowance: infantry and leaders have \texttt{5} MPs, cavalry has \texttt{7} MPs.
\end{itemize}

These are respectable rolls, but they still do not allow the Union columns to combine in the same battle.

\textbf{6. Union Movement Phase}

\begin{itemize}
\item Fremont advances aggressively and makes contact with Ewell's blocking force.
\item Shields continues to close on Port Republic, but he is still one turn away from being fully secure.
\item Because the Union columns are approaching from different directions, neither can materially assist the other in the battle about to occur.
\end{itemize}

\textbf{7. Combat Phase}

Only one significant battle is resolved this turn: Fremont against Ewell.

\textbf{Supply check.}

Both sides are supplied. Ewell can trace back to the Confederate wagon through the Confederate rear area, while Fremont traces to the Union logistical net behind him.

\textbf{Combat options.}

Fremont, trying to force the road, chooses \textit{Assault}. Ewell chooses \textit{Stand}. On the Combat Options Chart, that yields \texttt{2} rounds of combat unless one side demoralizes sooner.

\textbf{Wagon depletion.}

Because the Confederates did not choose \textit{Pitched Battle}, the wagon depletes only on a roll of \texttt{6}. The Confederate player rolls a \texttt{2}, so the wagon does not deplete.

\textbf{Commitment.}

\begin{itemize}
\item Fremont rolls moderately and commits a substantial part of his force, but not everything.
\item Ewell receives a favorable commitment result and commits enough troops to hold the line.
\end{itemize}

\textbf{Rounds of combat.}

\begin{itemize}
\item Round 1 produces moderate losses on both sides, but not enough to break the Confederates.
\item Round 2 inflicts additional losses on Fremont. The Union force does not collapse, but it also does not break through the Confederate position.
\end{itemize}

The key point is not annihilation. It is delay. Fremont has spent his turn fighting where Jackson wanted him to fight.

\textbf{8. Retreat and end of Turn 5}

Neither side is forced into a catastrophic retreat, but the Union has failed to clear the way in time. Ewell has done his job. Fremont is pinned west of the decisive point, and Jackson is free to deal with Shields on the next turn.

\textbf{Turn 6. Port Republic}

\textbf{1. Initiative Phase}

The Confederate player rolls a \texttt{2}. Again, that gives the Confederates the initiative.

\textbf{2. Confederate Command Phase}

Jackson rolls a \texttt{5} and receives \texttt{3} CPs. Against his command rating, that gives him full movement allowance and permits a force march if needed.

\textbf{3. Confederate Movement Phase}

Jackson now abandons the economy of force used on the previous turn and prepares the decisive blow.

\begin{itemize}
\item Jackson and Winder move together toward Shields.
\item Because more than two divisions are not moving together here, the stacking penalty is less burdensome than it was in the earlier Banks example.
\item Jackson force marches to ensure contact. After movement, the Confederate player makes the required attrition check under rule 7.52. In this example the die roll is low enough that no SPs are lost.
\item The wagon remains within supply distance of the attacking force instead of entering the combat hex.
\end{itemize}

Shields attempts reaction and fails. Jackson therefore enters the Union hex cleanly and sets up the decisive battle.

\textbf{4. Union Command and Movement Phase}

Shields has already been caught. He may still determine command for his own stack, but he cannot escape the battle that Jackson has forced.

In this example Shields receives only \texttt{1} CP. With a command rating of \texttt{3}, that yields about \texttt{33\%} movement allowance: infantry and leaders have \texttt{3} MPs, cavalry has \texttt{3} MPs. That is far too little to disengage cleanly or to reposition enough force to avoid combat.

Fremont is too far away, and still too occupied by Ewell, to influence the decisive battle this turn.

\textbf{5. Combat Phase}

The battle at Port Republic is now resolved.

\textbf{Supply check.}

Both sides are supplied.

\begin{itemize}
\item Jackson and Winder trace supply to the wagon kept just to the rear.
\item Shields traces to his own supply source.
\end{itemize}

\textbf{Combat options.}

Jackson chooses \textit{Pitched Battle}. Shields chooses \textit{Stand}. That means the battle will last \texttt{2} rounds unless one side demoralizes sooner.

\textbf{Wagon depletion.}

Because Jackson chose \textit{Pitched Battle}, the Confederate wagon depletes on a roll of \texttt{5} or \texttt{6}. The roll is \texttt{3}, so it remains undepleted through the battle.

\textbf{Commitment.}

\begin{itemize}
\item Jackson receives a strong commitment result and brings most or all of his available striking force into action.
\item Shields receives a weaker result and cannot commit enough strength to match the Confederate concentration.
\end{itemize}

\textbf{Round 1.}

\begin{itemize}
\item Confederate fire is strong because of high commitment, concentrated strength, Jackson's combat bonus, and the \textit{Pitched Battle} modifier.
\item Union return fire is meaningful but inferior.
\end{itemize}

At the end of the round the Union has lost more than \texttt{10\%} of its initial committed force, so it must check for demoralization.

\textbf{Demoralization.}

The Union demoralization roll fails. All participating Union combat units immediately become demoralized and must retreat.

Because the Union demoralizes after the first round, the battle ends at once even though the option pairing might otherwise have allowed a second round.

\textbf{6. Retreat}

Under rule 14.21 the retreating Union force receives \texttt{4} MPs of retreat without paying ZOC costs. The Union player retreats toward a legal line of withdrawal, but the result is still a sharp Confederate success. Since this is the decisive action of the scenario, the retreat effectively ends the Union chance to trap Jackson.

\textbf{7. Conclusion Phase}

\begin{itemize}
\item The Confederate wagon did not deplete, so it remains available.
\item The demoralized Union force may attempt recovery in the Morale Recovery Phase, but even a successful recovery would come too late to change the scenario result.
\item In a 1862 scenario, the players next apply the appropriate Panic Track adjustment.
\end{itemize}

\textbf{What this example showed.}

\begin{itemize}
\item Command-point rolls and movement allowances in the late campaign
\item The use of a holding action to delay one Union column
\item A force march into the decisive battle
\item Reaction failure at the decisive point
\item Supply traced to a wagon kept behind the front line
\item Combat options, commitment, and wagon depletion
\item Demoralization, retreat, and end-of-turn recovery
\item How Scenario 3 can culminate in a Cross Keys / Port Republic sequence
\end{itemize}

\end{document}
