\section{End of Turn}

When the Round marker cannot be advanced any further then the turn ends and the Turn marker advances. At the end of the second, third and fourth turns victory points are also scored. At the end of the fourth turn the game ends.

Reset the Round marker. The number of rounds is reduced by one every turn, i.e. on turn 2 there will be 9 action rounds, on turn 3 there will be 8 action rounds and on turn four there will be 7 action rounds.

Players score VP’s for controlling provinces and sea areas and by having trade markers in them.

\subsection{Victory Points}

A player with a control marker in an area/province scores VP equal to the VP value of the area/province.

The player with the most trade markers in an area/province scores VP equal to half, rounded down, of the area/province. If there is a tie for trade markers then no player gains these points.

Players must also reveal all the available Army cards they have in their possession, along with those already on display. Many of these cards have a negative value in the top right corner. These are the number of VP lost for holding that card.

Players receive one VP for every trade marker gained through plunder. These markers are then returned to the owning player.

Keep track of each player’s score on paper. At the end of the fourth turn, the scores from each player turn should be added together to create a final total. The player with the most VP’s wins.

The new first player is the player to the left of the previous first player, i.e. clockwise.