\subsection{Example of Combat}

John has decided that he wishes to attack Syria from his own province of Cappadocia. Syria is part of Geoff's empire. Both players now select five cards from their respective hands. John selects his cards and places them in a pile, facedown, in the following order:

\begin{enumerate}[nosep]
  \item Light Horse,
  \item Heavy Cavalry 7
  \item Pike 7
  \item Spear 7
  \item Foot Skirmisher
\end{enumerate}

Normally the Foot Skirmisher would have to be played before the Pike or Spear, as it is a fast unit. However, John has a Military Leader on display, which allows him to play one card out of sequence.

Geoff selects his cards and places them in the following order:

\begin{enumerate}[nosep]
  \item Light Horse
  \item Elephant 7
  \item Heavy Cavalry 7
  \item Pike 7
  \item Sword 7
\end{enumerate}

Each player now reveals the top card of their respective piles. Both players have played Light Horse, which results in a tie.

They each reveal their next card and Geoff has to roll a die to check whether or not his Elephant rampages. He rolls a 3, which means the unit is effective. Its strength is increased to 8 because it is facing a Cavalry unit, resulting in a score of 8-7, and a win for Geoff. He moves a battle marker to the defender’s side of the Battle Display.

The next cards are revealed and John’s Pike unit beats Geoff’s Heavy Cavalry since the Pike unit gains a +1 bonus against Heavy Cavalry units. John moves a battle marker to the attacker’s side of the Battle Display.

The next two revealed cards - Spear 7 and Pike 7 - result in a tie, so no markers are moved.

The last card of each player is now revealed. John rolls a die to see how effective his Foot Skirmishers are. He rolls a 6 which means he defeats the opposing unit and so moves a battle marker to his side of the display.

John has ended up with two battle markers to Geoff’s one marker, making John the winner. He replaces Geoff’s control marker in Syria with one of his own.

John must randomly lose one of the five cards that he played, since Geoff gained one battle marker. Geoff must randomly lose two cards since John gained two battle markers against him.
