\section{SETTING UP THE GAME}

Each player should select a set of control and trade markers, and one Warehouse card where you will store your trade markers (cubes). Your Warehouse is public information and should be kept in front of you.

There are six sets of Empire Army cards, marked from A to F, half with a green border, the remainder with a yellow border. These should be arranged into six piles, with the three green-bordered sets (North) placed at the top of the map and the other three sets (South) at the bottom of the map. Each set of three stacks should be turned face down and shuffled around so that players don’t know which set is which.

Roll a die to see who will become the 1st player (for purposes of setup only). In clockwise order, starting with the 1st player, each player places one control marker in a land province of their choice. As soon as you place a control marker you take one set of Empire cards. If the marker was placed in a northern province then you take one of the green-bordered sets at the top of the map. If placed in a southern province then you take one of the yellow-bordered sets at the bottom of the map. A maximum of three players can start in the north, and three players can start in the south. Any unclaimed decks are returned to the box, unexamined.

Players retain their Empire cards throughout the game. They form the backbone of their army and guarantee that a player will always have the minimum number of cards to fight a land battle (though not necessarily a sea battle).

\subsection{North and South}

Northern provinces are all those north of the Mediterranean and west to Asia Minor. Southern provinces are south of the Mediterranean and east of Thrace. Sicily is a northern province, while Crete and Cyprus are both southern provinces.

\subsection{Cards and Markers}

Shuffle the available Army cards and then lay out 6 cards, face up by the side of the map. Place the remaining deck at one end of the line of six cards.

Place a black marker on the first space of the Turn track and a black marker on the first space of the Round track. Place the three Battle Blocks in the “Center Ground” box of the Battle Display.