\section{Weather}\label{sec:11.0}

\ruleslabel{General Rule}

\begin{generalrule}

Game-Turns 4, 8, 12, and 16 are automatically Winter Game-Turns. In addition, during the Weather Phase of Game-Turns 2, 6, 10, and 14, the Yugoslav Player must determine if drought will exist in the ensuing year (the current and three successive Game-Turns).

\end{generalrule}

\subsection{Winter}\label{sec:11.1}

\case{11.11} During a Winter Game-Turn, the number of reinforcing guerrilla groups that are created by recruitment in Mountain triangles or village Objective Displays is halved (round fractions down). Exception: See Case 11.12.

\case{11.12} Yugoslav units occupying the Mountain triangles in the Islands Zone Display are not affected by Winter Game-Turns in terms of recruitment.

\subsection{Drought}\label{sec:11.2}

\case{11.21} During the Weather Phase of Game-Turns 2, 6, 10, and 14, the Yugoslav Player must roll a single die in order to determine if drought is created during the current Game-Turn and the following three Game-Turns.

\case{11.22} There are two possible weather results: drought and normal:

\textbf{A.} On Game-Turn 2, a die roll of 1 through 3 indicates drought, and a die roll of 4 through 6 indicates normal. Game-Turn 1 is normal.

\textbf{B.} On Game-Turns 6, 10, and 14, a die roll of 1 through 5 indicates a result opposite that in existence for the previous four Game-Turns (i.e., if Game-Turn 5 was drought and a 4 was rolled by the Yugoslav Player during the Weather Phase of Game-Turn 6, a normal result would be in effect through Game-Turn 9). A die roll of 6 indicates that the previous condition is repeated for the next four Game-Turns.

\case{11.23} If drought is created, the Game-Turn marker should be flipped over
to indicate this condition. If drought is in effect during a Guerrilla
Reinforcement Phase, the number of reinforcing guerrilla groups created by
recruitment in market town Objective Displays is halved (rounding fractions
down).

\case{11.24} Normal weather has no effect on any game function.
