\section{Yugoslav Victory Points}\label{sec:14.0}

\ruleslabel{General Rule}

\begin{generalrule}
The Yugoslav Player (only) accumulates and loses Victory Points during the Victory Point Stage. The number of Victory Points accumulated by the Yugoslav Player at the end of the game will determine the winner. In addition, the accumulation of a certain number of Victory Points during the course of the game will trigger events altering the game’s flow.
\end{generalrule}

\ruleslabel{Cases}

\subsection{How Yugoslav Victory Points Are Recorded}\label{sec:14.1}

\case{14.11} Yugoslav Victory Points are recorded on the Victory Point Track (14.13) only during the Victory Point Stage. At this time, the Yugoslav Player should examine the map, checking to see if any of the conditions of Cases 14.2 and 14.3 are fulfilled — accumulating and deducting Victory Points according to the instructions of these Cases.

\case{14.12} Yugoslav Victory Points are recorded with the appropriate markers on the Victory Point Track. As each condition of Cases 14.2 and 14.3 is fulfilled, these markers should be adjusted appropriately. Each Victory Point marker is printed with a positive and negative side. (It is permissible for the Victory Point total to go into negative figures; if it does, simply flip the markers over to their negative sides.)

\case{14.13} Victory Point Track (see mapsheet)

\subsection{How The Yugoslav Player Accumulates Victory Points}\label{sec:14.2}

The fulfillment of the following conditions accumulates Victory Points for the Yugoslav Player during the Victory Point Stage of each Game-Turn:

\textbf{A.} The Yugoslav Player should check each Objective Display currently occupied by at least one Yugoslav (or Soviet or pro-Yugoslav Bulgarian) unit. For each occupied Objective Display, the

Yugoslav Player receives the Victory Point Value of that Display (the second Value printed in the Axis box).

\textbf{B.} The Yugoslav Player should check every Yugoslav (or Soviet or pro-Yugoslav Bulgarian) occupied Mountain triangle separately. The number of Yugoslav Strength Points in each such occupied Mountain should be totalled and divided by four (round fractions down). The result is the number of Victory Points awarded to the Yugoslav Player. However, no more Victory Points may be awarded per Mountain triangle than the number of units currently occupying the triangle. Example: If one Partisan division (Strength of 12) and nine Chetnik groups (each with a Strength of 1) occupy their respective Mountain triangles in Istria, the Yugoslav Player would receive 1 Victory Point for the Partisan division and 2 Victory Points for the Chetnik groups.

\textbf{C.} The Yugoslav Player receives 5 Victory Points for each German unit that is currently on the map after its scheduled transfer (see 13.7).

\subsection{How The Yugoslav Player Loses Victory Points}\label{sec:14.3}

The Yugoslav Player should deduct Victory Points due to the fulfillment of the following conditions during the Victory Point Stage:

\textbf{A.} If Tito is currently withdrawn from the map (see 9.43), the Yugoslav Player loses 5 Victory Points.

\textbf{B.} If Tito has been eliminated (see 9.43), the Yugoslav Player loses 25 Victory Points in the ensuing Victory Point Stage and 5 Victory Points in every succeeding Victory Point Stage.

\textbf{C.} If, at the beginning of the immediately preceding Yugoslav Movement Phase, there were no Chetnik guerrillas on the map, the Yugoslav Player loses 5 Victory Points. If there were no Chetnik units of any allegiance, the Yugoslav Player loses 15 Victory Points instead. After Allied Support Withdrawal, this Case is ignored.

\textbf{D.} If, at the beginning of the immediately preceding Yugoslav Movement Phase (except on Game-Turn 1), there were no Partisan units on the map, the Yugoslav Player loses 25 Victory Points.

\textbf{E.} For each Soviet and pro-Yugoslav Bulgarian unit on the map during the Victory Point Stages' of Game-Turns 16 and 17, the Yugoslav Player loses 20 Victory Points.

\textbf{F.} If any of the three optional Soviet reinforcements have been deployed by the Yugoslav Player in the immediately preceding Yugoslav Movement Phase (see 13.92), the Yugoslav Player loses 5 Victory Points for each one deployed.

\subsection{Events Triggered By Yugoslav Victory Points}\label{sec:14.4}

A number of events are triggered by the first accumulation of 45 Victory Points by the Yugoslav Player (or the first appearance of a Yugoslav brigade on the map). These events are described in Cases 6.64, 9.41, and 13.91D.
