\section{REINFORCEMENT SCHEDULES}

\subsection{SOVIET REINFORCEMENTS}

The following are the schedule Soviet reinforcements; these are in addition to Soviet Provisional Reinforcements (see Case 14.1) and South-Western Front Reinforcements (see Case 14.2). Reinforcement arrival is indicated on the Turn Record Track.

\begin{flushleft}
  \textbf{Enter on Game-Turn One on Entrance Hex X:}
  6 Rifle Divisions; General \textbf{Rokassovski}.
  \break
  \textbf{On Entrance Hex V:}
  \break
  22nd Army (5 Rifle Divs.; Gen. \textbf{Yershakov}).

  \textbf{Enter on Game-Turn Two on Entrance Hex W:}
  30th Army (3 Rifle Divs; 1 Armd. Div.; Gen. \textbf{Khomenko}).
  \break
  \textbf{On Entrance Hex X:}
  \break
  4 Rifle Divisions.

  \textbf{Enter on Game-Turn Three on Entrance Hex Z:}
  21st Army (5 Rifle Divs.; 2 Armd Divs.; Gen. \textbf{Gerisamenko}).
  \break
  \textbf{On Entrance Hex X:}
  \break
  4 Rifle Divisions.

  \textbf{Enter Game-Turn Four on Entrance Hex X:}
  28th Army (5 Rifle Divs.; 1 Armd Div.; Gen. \textbf{Kachalov}).

  \textbf{Enter Game-Turn Five on Entrance Hex X:}
  \break
  4 Rifle Divs.; 1 Armd Div.

  \textbf{Enter Game-Turn Six on Entrance Hex X:}
  \break
  4 Rifle Divisions.

  \textbf{Enter Game-Turn Seven on Entrance Hex X:}
  \break
  29th Army (4 Rifle Divs.; Gen. \textbf{Maslennlkov}).

  \textbf{Enter Game-Turn Eight on Entrance Hex X:}
  \break
  31st Army (4 Rifle Divs.; Gen. \textbf{Dolmatov}).

  \textbf{Enter Game-Turn Nine on Entrance Hex X:}
  \break
  49th Army (4 Rifle Divs.; Gen. \textbf{Zakharkln}).

  \textbf{Enter Game-Turn Ten on Entrance Hex X:}
  \break
  32nd Army (4 Rifle Divs.; Gen. \textbf{Vishnevsky}).

  \textbf{Enter Game-Turn Eleven on Entrance Hex X:}
  \break
  33rd Army (4 Rifle Divs.; Gen. \textbf{Onuprlenko}).
\end{flushleft}

\subsection{GERMAN REINFORCEMENTS}

\begin{flushleft}
  \textbf{Enter Game-Turn One In Entrance Area C:}
  \break
  39th Panzer Corps (7th Pz, 12th Pz, 14th Mot Inf,
  20th Mot Inf, 20th Pz Divs.).

  \textbf{Enter Game-Turn Two In Entrance Area A:}
  \break
  57th Panzer Corps (l8th Mot Inf, 19th Pz Divs, Lehr PzGr Rgt).
  \break
  \textbf{In Entrance Area B:}
  \break
  6th and 16th Infantry Divisions.

  \textbf{Enter Game-Turn Three In Entrance Area D:}
  \break
  5th, 35th and 161st Infantry Divisions.
  \break
  \textbf{In Entrance Area E:}
  \break
  47th Panzer Corps (29th Mot Inf, 17th Pz, 18th Pz).
  46th Panzer Corps (lOth Pz, SS Das Reich Mot Inf, Divs.; Gross Dtschld PzGr Rgt).
  \break
  \textbf{In Entrance Area H:}
  24th Panzer Corps (3rd Pz, 4th Pz, 10th Mot Inf Divs.; 1st Cavalry Division).

  \textbf{Enter Game-Turn Five In Entrance Area E:}
  \break
  263rd. 137th and 23rd Infantry Divisions.

  \textbf{Enter Game-Turn Six In Entrance Area E:}
  \break
  258th and 292nd Infantry Divisions.

  \textbf{Enter Game-Turn Seven In Entrance Area E:}
  \break
  7th. 15th and 17th Infantry Divisions.

  \textbf{Enter Game-Turn Eight In Entrance Area F:}
  \break
  252nd and 78th Infantry Divisions.

  \textbf{Enter Game-Turn Nine In Entrance Area G:}
  \break
  31st and 34th Infantry Divisions.
\end{flushleft}