\section{SEQUENCE OF PLAY}

\subsection{THE GAME-TURN}

\textbf{Panzergruppe Guderian} is played in Game-Turns; there are twelve Game-Turns in a complete game. Each Game-Turn is composed of two Player-Turns. The Player whose Player-Turn is in progress is called the Phasing Player. Each Game-Turn proceeds strictly as follows.

\subsection{GAME-TURN SEQUENCE OUTLINE}

A. SOVIET PLAYER TURN

\textbf{1. Movement Phase:} The Soviet Player checks for Supply; he then moves any or all of his units in any direction or directions, to the limit of each unit's Movement Allowance, and within the restrictions outlined in the Rules of Movement and Supply. The Soviet Player may conduct Overruns in this Phase. He also brings in his Reinforcements according to the Reinforcement Schedule. At the end of this Phase, German Air Interdiction Markers are removed.

\textbf{2. Combat Phase:} Soviet units may attack German units according to the Rules of Combat.

\textbf{3. Disruption Removal Phase:} The Soviet Player may remove all Disruption Makrers from units that have suffered Disruption as a result of Overrun.

\textbf{4. Soviet Interdiction Phase:} The Soviet Player may choose this Turn as one of the three Turns in the game in which he may use Interdiction. If he does, he places his Interdiction Marker on the game map according to the Rules for Soviet Interdiction.

B. GERMAN PLAYER TURN

\textbf{1. Initial Movement Phase:} The German Player checks for Supply. He may then move his units, bring in reinforcements, and conduct Overruns.

\textbf{2. Combat Phase:} German units may attack Soviet units.

\textbf{3. Mechanized Removal Phase:} German Panzer, Mech, Motorized and Cavalry units may move again, if possible. German units may conduct Overruns in this Phase.

\textbf{4. Disruption Removal Phase:} The German Player removes any Disruption Markers from his units.

\textbf{5. Air Interdicition Phase:} The German Player may place his Air Interdiction Markers on the game map according to the rules for Air Interdiction. He may remove any Soviet Interdiction Markers on the game map.

C. GAME-TURN INDICATION

AFter both Players have completed their respective Player-Turns, the Game-Turn is completed. The Game-Turn Marker is advanced on the Game-Turn Record Track, signalling the start of a new Game-Turn.