\section{STACKING}

\subsection{SOVIET RESTRICTIONS}

The Soviet Player may never have more than three \textbf{combat} units in any one hex at the end of his Movement Phase and at \textbf{any} time during the Combat Phase. He may have as many as four units of \textbf{any} kind in a hex, as long as at least one of the units is a Leader. Informational Markers, such as German Air Interdiction Markers and Disrupted Markers, never count against stacking. Units may pass freely through other stacks of Friendly units, except during retreats, and the restrictions of stacking apply only at the end of the Friendly Movement Phase and throughout all Combat Phases. If units are found to be in excess of the stacking restrictions at the end of a Friendly Movement Phase or any Combat Phase, the excess must be eliminated and removed from the game, at the choice of the Owning Player.

\subsection{GERMAN RESTRICTIONS}

The German Player may never have more than three combat units in any one hex at the end of either of his Movement Phases or at the end of any Combat Phase. The same penalties for overstacking as apply to the Soviets (7.1) apply to the Germans.

\begin{flushleft}
  \subsection{GERMAN DIVISIONAL INTEGRATION}
\end{flushleft}

If the German Panzer, Mech, or Motorized units in a hex comprise \textbf{all} the units of a division, the total Strength of the units in that hex is doubled for both attack and defense. There may not be any units from any other division in that hex, and \textbf{all} units from the division must be in the hex. Each Panzer Division has one Panzer and two Panzer Grenadier regiments, and each Motorized Infantry Division has two regiments, with the exception of the \textbf{Das Reich} Motorized Infantry Division, which has three regiments. German Infantry and Cavalry Divisions do not qualify for this combat bonus. If any regiment in a division is eliminated, the combat bonus may not be used by that division.