\section{UNTRIED UNITS}

GENERAL RULE:

The Combat Strengths of \textbf{Soviet} units that have yet participated in combat are unknown to both the Soviet and German players. All Soviet units are initially placed with their Untried side face-up. This does not apply to Leaders. As the game progresses and opposing units have combat with one another, the Strengths of the Soviet units will be revealed by inverting the counter.

CASES:

\begin{flushleft}
  \subsection{PLACEMENT OF UNTRIED UNITS}
\end{flushleft}

All Soviet combat units, whether they start the game on the game map or enter as reinforcements, are placed on the game map in their Untried state. Units are picked by type (Rifle or Tank/Mech Division) from the pool of provided counters. Neither the Soviet nor the German Player should be aware of the actual Strengths of the units until they are revealed.

\subsection{HOW UNITS ARE REVEALED}

Once the units are placed and play begins, units remain in their Untried state until they are involved in combat. Once a unit has been committed to combat, the true Strength of the unit is revealed; however, the moment of revelation comes only at the \textbf{instant} of combat; i.e., neither Player may see what the actual Strengths of the Soviet units are until it is time to throw the die for that particular combat. Once Soviet units have been committed to combat, they may not be withdrawn or re-allocated, even if the odds are unfavorable (however, see Case 12.3).

\subsection{NO STRENGTH UNITS}

Certain Soviet combat units have no Attack or Defense Strengths. These units are removed from the game at the instant of revelation, as they can neither attack nor defend. However, as long as they remain in an Untried state, they have a Zone of Control and block Supply and retreat lines, etc. There are two Soviet Rifle Divisions with a Combat Strength of 0-1-6. These units are \textbf{not} removed upon revelation; however, they may never attack, only defend. If committed to an attack prior to revelation, they must retreat in a fash similar to a Leader unit (see Case 10.23).

\subsection{ELIMINATED UNTRIED UNITS}

All Soviet units that are eliminated in combat or removed from the game because they have no Combat Strength (0-0-6) are placed in a separate pile in an inverted, Untried state. When the Soviet Player has run out of reinforcements from the counters provided, he may pick reinforcements from this "dead pile" until he has used all counters available to him and there are no other counters available to him and there are no other counters to use. The Soviet Player is limited to the number of counters he actually receives by the number of counters provided.
